SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Improve the last paragraph of the introduction

To address these two issues,
we developed SimBio,
a Python package to define and simulate reaction networks.
From the end-user point of view,
it is focused on providing an ergonomic experience
by integrating well with IDEs and static analysis tools
through the use of standard modern Python syntax.
From the power-user point of view,
it can be extended from Python,
since its coded in pure Python.
Finally,
from the developer/maintainer point of view,
it has a modular architecture with a clear separation of concerns,
making it easier to maintain or to contribute new code.

the models can be easily introspected,
and simulation extended from Python.
Clean API to create tools (graphs, tables, etc)

@@

>>>>

To address these two issues,
we developed SimBio,
a Python package to define and simulate reaction networks.
From the end-user point of view,
it is focused on providing an ergonomic experience
by integrating well with IDEs and static analysis tools
through the use of standard modern Python syntax.
From the power-user point of view,
since its coded in pure Python,
it can be extended from Python.
Its models can be introspected to create other representations
such as graphs connecting species and/or reactions,
or tables with parameters or equations.
Finally,
from the developer/maintainer point of view,
it has a modular architecture with a clear separation of concerns into three packages,
making it easier to maintain or to contribute new code.

@@

We have written a set of Python packages
that allow to define and simulate dynamical systems and reaction networks.
Thay have a modular architecture that makes them easy to extend in different points.

Poincaré and SimBio are focused on their integration with IDE
